Full Dissertation

### 2024-04-04 Sections/full.qmd
re-render with updated gen discussion

@@

## Comparison to Project 1

### Differences between the tasks

There are a number of differences between Project 1's Hit The Target (HTT), and Project 2's Hit The Wall (HTW) tasks.

- Task Space Complexity: In HTW, the task space is also almost perfectly smooth, at least for the continuous feedback subjects, if they throw 100 units too hard, they'll be told that they were 100 units too hard. Whereas in HTT,  it was possible to produce xy velocity combinations that were technically closer to the empirical solution space than other throws, but which resulted in worse feedback due to striking the barrier.

- Perceptual Distinctiveness: HTT offers perceptually distinct varied conditions that directly relate to the task's demands, which may increase the sallience between training positions encounted by the varied group. In contrast, HTW's varied conditions differ only in the numerical values displayed, lacking the same level of perceptual differentiation. Conversely in HTW, the only difference between conditions for the varied group are the numbers displayed at the top of the screen which indicate the current target band(e.g. 800-1000, or 1000-1200)

- In HTW, our primary testing stage of interest has no feedback, whereas in HTT testing always included feedback (the intermittent testing in HTT expt 1 being the only exception). Of course, we do collect testing with feedback data at the end of HTW, but we haven't focused on that data at all in our modelling work thus far. It's also interesting to recall that the gap between varied and constant in HTW does seem to close substantially in the testing-with-feedback stage. The difference between no-feedback and feedback testing might be relevant if the benefits of variation have anything to do with improving subsequent learning (as opposed to subsequent immediate performance), OR if the benefits of constant training rely on having the most useful anchor, having the most useful anchor might be a lot less helpful if you're getting feedback from novel positions and can thus immediately begin to form position-specific anchors for the novelties, rather than relying on a training anchor.

- HTW and HTT both have a similar amount of training trials (~200), and thus the constant groups acquire a similar amount of experience with their single position/velocity in both experiments. However, the varied conditions in both HTT experiments train on 2 positions, whereas the varied group in HTW trains on 3 velocity bands. This means that in HTT the varied group gets half as much experience on any one position as the constant group, and in HTW they only get 1/3 as much experience in any one position. There are likely myriad ways in which this might impact the success of the varied group regardless of how you think the benefits of variation might be occurring, e.g. maybe they also need to develop a coherent anchor, maybe they need more experience in order to extract a function, or more experience in order to properly learn to tune their c parameter.

>>>>

## Project 2 Discussion

@@

## General Discussion

To facilitate ease of comparison between the two projects and their respective tasks, we'll now refer to project 1 as Hit The Target (HTT) and project 2 as Hit The Wall (HTW).

### Empirical Results Summary

Across two projects, we investigated the influence of training variability on learning and generalization in visuomotor tasks. In Project 1 (HTT), we consistently found that varied training led to superior performance relative to constant training, even when testing at positions that were identical to the constant group's training. In contrast, Project 2 (HTW) found the opposite pattern - the varied training groups exhibited poorer performance than the constant groups, both in terms of final training accuracy and the ability to accurately extrapolate to novel velocity bands during testing. This detrimental effect of variability was observed across three experiments, with the exception of the reverse order condition in Experiment 3, where the varied group was able to match the constant group's performance.

### Differences between the two Projects

Although the HTT and HTW tasks are similiar in requiring participants to learn how to correctly launch projectiles,  they nevertheless differ across numerous dimensions that may be relevant to the opposing patterns observed in the two projects (see @tbl-task-diff provides for a detailed comparison of the two tasks).

In HTT, the salient perceptual elements of the task (i.e. the launching box, target and barrier) are subject to variation (i.e. different distances between the launching box and target), and the spatial layout of these perceptually variable elements are intrinsically linked to the task objective of striking the target. Conversely, the perceptual task elements in HTW are invariant across trials, and the task objective is specified by the target velocity value specified as a numeral at the top of the screen. If the benefits of training variation do arise from the formation and flexible retrieval of distinct memory traces, then the lack of perceptual salience between training instances in the HTW task may have limited any potential benefits of variability. Future work could investigate this possibility further employing a modified version of the HTW task wherein the correct velocity value is indicated by some perceptual feature of the task (e.g. the color of the wall, or size of the ball), rather than displaying the target velocity numerically.

The HTT and HTW tasks also differed in terms of general task complexity. The HTT task was designed to mimic projectile launching tasks commonly employed in visuomotor learning studies, and the parabolic trajectories necessary to strike the target in HTT were sensitive to both the x and y dimensions of the projectiles velocity (and to a lesser extent, the position within the launching box at which the ball was released). Conversely the HTW task was influenced to a greater extent by the tasks commonly utilized in the function learning literature, wherein the correct output respones are determined by a single input dimension.

::: {#tbl-task-diff}

| Dimension                                       | HTT (Project 1)                                                                                                                               | HTW (Project 2)                                                                                                |
| ----------------------------------------------- | --------------------------------------------------------------------------------------------------------------------------------------------- | -------------------------------------------------------------------------------------------------------------- |
| Task Description                                | Projectile launching to hit a target                                                                                                          | Projectile launching to hit wall at a specific velocity                                                        |
| Task Complexity                                 | More complex parabolic trajectory, both x and y velocities relevant to outcome                                                                | Simpler 1D mapping of force to outcome. Only x velocity is relevant.                                           |
| Task Space                                      | More complex: xy velocity combinations closer to the solution space may still result in worse feedback due to striking the barrier.           | Simpler: smooth, linear mapping between velocity and feedback.                                                 |
| Perceptual salience of Varied Conditions | Varied conditions (# of throwing distances) are perceptually distinct, i.e. salient differences in distance between launching box and target. | Varied conditions (# of velocity bands) are less salient - only difference is the numeral displayed on screen. |
| Testing Feedback                                | Testing always included feedback                                                                                                              | Primary testing stage had no feedback.                                                                         |
| Potential for Learning during Testing           | Limited potential for learning during testing due to feedback.                                                                                | Some potential for learning during no-feedback testing by observing ball trajectory.                           |
| Position/Velocity Experience                    | Varied group gets half as much experience on any one position as the constant group.                                                          | Varied group gets 1/3 as much experience on any one velocity band as the constant group.                       |
| Testing Structure                               | Random interleaving of trained/transfer testing distances.                                                                                    | Blocked structure, separately testing trained vs extrapolation testing bands.                                  |

Comparison of the tasks in Project 1 (HTT) and Project 2 (HTW).
:::
